Quantitative Benchmarking for Automatically Generated Conjectures

### 2017-10-04 TEBenchmarkPaper/article.tex
Flesh out section 3

Unfortunately, uniform sampling of definitions gives rise to a lottery, where
for a large corpus and a fixed sample size, it becomes highly unlikely that a
sample will contain the particular definitions required by a theorem. This would
cause most samples to have an empty ground truth, and hence $0$ precision and
undefined recall \emph{independent} of what the ATE system produces. This is
clearly undesirable as an evaluation method.

Instead, we only choose samples which admit at least one of the corpus theorems.
We could do this using rejection sampling, but it is more efficient to sample
the \emph{theorem statements}, weighted in proportion to the number of
definitions they reference. Once a theorem is chosen, we use the referenced
definitions as our sample, padding uniformly up to the required size (we ignore
theorems which reference more definitions than our sample size).

@@

Given a sample of definitions and a corresponding ground truth, the actual
execution of the ATE system proceeds as in prior work. We must translate the
definitions into the required input format, which depends on the particular
tool being studied, then we time the execution, with a cutoff after e.g. 1 hour.

In our experiments we have found that memory usage also plays an important role,
but rather than introducing an extra dimension we can account for this by simply
allowing the system

@@

>>>>

Unfortunately, uniform sampling of definitions gives rise to a lottery: for a
large corpus and a fixed sample size, it becomes highly unlikely that a sample
will contain the particular definitions required by a theorem. This would cause
most samples to have an empty ground truth, and hence $0$ precision and
undefined recall \emph{independent} of what the ATE system produces. This is
clearly undesirable as an evaluation method.

Instead, we only choose samples which admit at least one of the corpus theorems.
We could do this using rejection sampling, but it is more efficient to sample
the \emph{theorem statements}, weighted in proportion to the number of
definitions they reference. Once a theorem is chosen, we use the referenced
definitions as our sample, padded up to the required size by uniformly sampling
from the remaining definitions (we ignore theorems which reference more
definitions than our sample size).

@@

Given a sample of definitions and a corresponding ground truth, the actual
execution of the ATE system proceeds as in prior work. We must translate the
chosen definitions into the particular input format of the tool under study,
then we time the execution, with a timeout after e.g. 1 hour.

In our experiments we have found that memory usage is also important, but rather
than complicating our analysis with an extra dimension, we instead set a limit
(as large as practical) and terminate program runs which cross it.~\footnote{We
  could treat the hardware's RAM capacity as our limit, allow the operating
  system to swap any overflow to disk, and wait for the inevitable slowdown to
  trigger the timeout. This requires no work to implement, but wastes a lot of
  time waiting for runs which could otherwise be terminated early.}

This approach process produces a single runtime, precision and recall value for
each sample. We propose two methods for analysing this data: \emph{summarising}
the performance of an ATE system, or \emph{comparing} the performance of
\emph{two} ATE systems.

\subsection{Summarising}

 - Giving each run a different sample is important for getting independent
   values which test the generality of the system. This is preferable to e.g.
   timing each sample multiple times.

 - What sorts of aggregate data to report: median vs mean, variance, quartiles,
   etc.

\subsection{Comparison}

To encourage competition in the field, it is important to compare the relative
performance of different ATE systems on the same task. Since the aggregate
statistics in the above summaries do not include details of specific runs, any
comparison based on them would have very low statistical power.

To produce more salient results, we should compare the data points directly, for
example with a \emph{paired difference test}: for each individual sample, we
find the \emph{difference} between the two systems' data \emph{for that sample}.
We then aggregate these differences, to determine whether one system performs
significantly better or worse than the other.

 - Good because: handles the variance of results well
 - Good because: approximates a normal distribution, making meaningful statistics easier
 - Good because: conservative in the face of timeouts

 - Question: do we use relative difference, e.g. [ 1.0:1.2, 1.0:1.5, ...], or do
   we use absolute differences, e.g. [100s:120s, 1s:1.5s, ...]?

@@

To aid reproducibility, we use a cryptographic hash as our source of randomness:
the $n$th sample of size $s$ uses the SHA256 hash of $n$, $s$ and the definition
corpus; the latter prevents tailoring the corpus to influence the choices,
although ATE systems could .
